---
title: "Variable selection using R"
author: "Prince John"
date: "25/12/2020"
output: pdf_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## Loading data

```{r message=FALSE, warning=FALSE}
library(dplyr)
library(readr)
library(ggplot2)
library(lares)
library(modelr)
```


```{r houseData}
diabData<-read.csv('diabetes.csv',header = T)

```

## Full and Base models
Our full model is
```{r}
response=diabData[,dim(diabData)[2]]
predictorX=diabData[,1:(dim(diabData)[2]-1)]
fullModel = lm(response~predictorX[,1]+predictorX[,2]
	+predictorX[,3]+predictorX[,4]+predictorX[,5]
	+predictorX[,6]+predictorX[,7]+predictorX[,8]) 
```
and the base model is 


```{r}
baseModel = lm(response~1)
```

Let's have a look at the coefficients

```{r}
fullModel$coefficients
```
Now, we are interested in the forward stepwise addition and the backward stepwise deletion to see which variables are good.

## Forward Stepwise addition

```{r}
step(baseModel,scope=list(upper=fullModel,lower=~1),direction="forward")
```
The last part shows the best variables as $X_2,X_6,X_1,X_7,X_3,X_8$

## Backward stepwise deletion

```{r}
step(fullModel, direction="backward")
```
We get the best set of attributes there as well.

